Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-07 R0V0.tex
Propagate changes on notation to the example

\mypara Once a solution to MI~\eqref{eq:MI formulation} has been computed, the function defined, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, by
	\begin{equation}\label{eq:differential feedback law}
		\delta_k=Y(x,u)W^{-1}(x)\delta_x:=K(x,u)\delta_x
	\end{equation}
	is a differential feedback law that renders the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop with $\delta_k$.

@@

\mypara Define $\Xi$ as the set of functions $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ with components defined by
\begin{equation*}
		Y_{ij}(\cdot)\begin{cases}
		=Y_{ij}(x_i,\vec{x}_i)u_i\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
		\equiv0_{m_i\times n_i},&\text{otherwise},
		\end{cases}
\end{equation*}
for every $i,j\in\mathscr{V}_c$, and for every $(x_i,\vec{x}_i,u_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}\times\mathbb{R}^{m_i}$.

@@

\mypara In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $i\in\mathbb{N}_{[1,4]}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\mathbb{R}^8$, $\mathbf{C}(i)=\mathbb{R}^8$. The parser took 98  seconds to solve the MI~\eqref{eq:MI:SSCCM}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-2y_i\;,\\
 \underline{Y}_{ij}(q)=&-2-2\sum_{k=1}^4 y_k^2+x_k^2\;.
\end{align*}

\begin{figure*}
\begin{equation}\label{eq:example:Y:general}
		Y(q)=\begin{bmatrix}
			\overline{Y}_{11}(q),&\underline{Y}_{12}(q),&0,&0,&-0.03y_1,&0,&0&0\\
			0,&0,&\overline{Y}_{23}(q),&\underline{Y}_{24}(q),&0,&0,&-0.04y_2,&0\\
			-0.04y_3,&0,&0,&0,&\overline{Y}_{35}(q),&\underline{Y}_{36}(q),&0,&0\\
			0,&0,&-0.03y_4,&0,&0,&0,&\overline{Y}_{47}(q),&\underline{Y}_{48}(q)
		\end{bmatrix}
\end{equation}
\end{figure*}

@@

\mypara In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. To comply with this requirement, the set $\mathscr{K}$ is defined as $\mathscr{K}(1)=\{1,2\}$, $\mathscr{K}(4)=\{3,4\}$ and $\mathscr{K}(i)=\{i-1,i,i+1\}$, for each index $i=2,3$. The sets $\mathbf{C}$ are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}(1)&=&\{\begin{bmatrix}
		1,&1,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(2)&=&\{\begin{bmatrix}
		1,&1,&1,&1,&1,&1,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(3)&=&\{\begin{bmatrix}
		0,&0,&1,&1,&1,&1,&1,&1\end{bmatrix}\},\\
		\mathbf{C}(4)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&1,&1,&1,&1\end{bmatrix}\}\;.
	\end{array} 
\end{equation*}

\mypara The sets $\mathbin{\mathtt{proj}}_{\mathscr{K}}(\mathbb{R}^8)$ are defined, for each index $i\in\mathbb{N}_{[1,4]}$, as
\begin{equation*}
	\begin{array}{rcl}
		\mathbin{\mathtt{proj}}_{\mathscr{K}(1)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
		q_1,&q_2\end{bmatrix}\}\;,\\
		\mathbin{\mathtt{proj}}_{\mathscr{K}(2)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
		q_1,&q_2,&q_3\end{bmatrix}\}\;,\\
		\mathbin{\mathtt{proj}}_{\mathscr{K}(3)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
		q_2,&q_3,&q_4\end{bmatrix}\}\;,\\
		\mathbin{\mathtt{proj}}_{\mathscr{K}(4)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
		q_3,&q_4\end{bmatrix}\}\;.
	\end{array}
\end{equation*}

\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
\begin{equation}\label{eq:example:Y:neighbor and decentralized}
	 Y(q)=\begin{bmatrix}
 	\overline{Y}_1(\cdot)&0&0&0\\
 	0&\overline{Y}_2(\cdot)&0&0\\
 	0&0&\overline{Y}_3(\cdot)&0\\
 	0&0&0&\overline{Y}_4(\cdot)
 \end{bmatrix}\;,
\end{equation}
with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
\begin{equation*}
	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}, i\in\mathbb{N}_{[1,4]}\;.
\end{equation*}

\mypara In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI:SSCCM} was 2.6 seconds. In this case, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\{q_i\}$. Moreover, the sets $\mathbf{C}$ are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}(1)&=&\{\begin{bmatrix}
		1,&1,&0,&0,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(2)&=&\{\begin{bmatrix}
		0,&0,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(3)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&1,&1,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(4)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&0,&0,&1,&1\end{bmatrix}\}\;.
	\end{array} 
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the matrix $W$ 
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
\end{align*}

>>>>

\mypara Once a solution to MI~\eqref{eq:MI formulation} has been computed, the function defined, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, by
	\begin{equation}\label{eq:differential feedback law}
		\delta_k=Y(x,u)W^{-1}(x)\delta_x:=K(x,u)\delta_x
	\end{equation}
	is a differential feedback law that renders the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop with $\delta_k$.

@@

\mypara Define $\Xi$ as the set of functions $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ with components defined by
\begin{equation*}
		Y_{ij}\begin{cases}
		=Y_{ij}(x_i,\vec{x}_i)u_i\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
		\equiv0_{m_i\times n_i},&\text{otherwise},
		\end{cases}
\end{equation*}
for every $i,j\in\mathscr{V}_c$, and for every $(x_i,\vec{x}_i,u_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}\times\mathbb{R}^{m_i}$.

@@

\mypara In the first one, the graph $\mathscr{G}_c$ describing the communication network is fully connected, i.e., $\mathscr{E}_c=\mathbb{N}_{[1,4]}\times\mathbb{N}_{[1,4]}$ and no constraints were imposed on the matrix $Y$. Consequently, for each $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{1,2,3,4\}$, and for every $j\in\mathbb{N}_{[1,4]}$, $Y_{ij}=Y_{ij}(q_1,\ldots,q_4)\in\mathbb{R}^{1\times 2}$.

The parser took 98  seconds to solve the MI~\eqref{eq:MI:SSCCM}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has elements defined, for every $q\in\mathbb{R}^8$, by
\begin{align*}
	\overline{Y}_i(q)=&-2\begin{bmatrix}
	y_i&1+\sum_{k=1}^4 y_k^2+x_k^2
	\end{bmatrix},\\
	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},
\end{align*}
where $i\in\mathbb{N}_{[1,4]}$, and structure given by the matrix
\begin{equation}\label{eq:example:Y:general}
		\resizebox*{0.85\columnwidth}{!}{$\begin{bmatrix}
			\overline{Y}_1(q),&0_{1\times 2},&-0.03\hat{Y}_1(q),&0_{1\times2}\\
			0_{1\times 2},&\overline{Y}_2(q),&0_{1\times 2},&-0.04\hat{Y}_2(q)\\
			-0.04\hat{Y}_3(q),&0_{1\times 2},&\overline{Y}_3(q),&0_{1\times 2}\\
			0_{1\times 2},&-0.03\hat{Y}_4(q),&0_{1\times 2},&\overline{Y}_4(q)
		\end{bmatrix}$}.
\end{equation}

@@

\mypara In the ``neighbor'' case, the communication network topology $\mathscr{G}_c$ has the same structure as the network system. Consequently, the sets $\mathscr{K}$ are defined as $\mathscr{K}(1)=\{1,2\}$, $\mathscr{K}(4)=\{3,4\}$ and $\mathscr{K}(i)=\{i-1,i,i+1\}$, for each index $i=2,3$.

\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
\begin{equation}\label{eq:example:Y:neighbor and decentralized}
	 Y(q)=\begin{bmatrix}
 	\overline{Y}_1(\cdot)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&\overline{Y}_2(\cdot)&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&\overline{Y}_3(\cdot)&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_4(\cdot)
 \end{bmatrix}\;,
\end{equation}
with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
\begin{equation*}
	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}, i\in\mathbb{N}_{[1,4]}\;.
\end{equation*}

\mypara In the fully decentralized case, also the communication network topology $\mathscr{G}_c$ has the same structure as the network system. However, the sets $\mathscr{K}$ are defined as proper subsets of $\mathscr{E}$. More precisely, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$. The time taken by the parser to solve the MI~\eqref{eq:MI:SSCCM} was 2.6 seconds, the matrix $W$ is given by
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
\end{align*}
